---
title: "Hypothesis Testing"
output: html_notebook
author: Kelly Rivera
---

# Exploring eSports Earnings

Data set: eSports Earnings: Money earned by Players & Teams from eSports Tournaments

## Install & load libraries
```{r}
#Install tidyverse
#install.packages("tidyverse")

#load libraries
library(tidyverse)
library(ggplot2)
```


## Import Dataset CSV
```{r}
# Importing the csv file
esports <- read_csv("highest_earning_teams.csv")
head(esports, 5)
```

## Exploring the data
```{r}
# Dropping these games from the data set 
Esports <- esports[esports$Game != "Arena of Valor" & esports$Game != "Starcraft II", ] 

#Renaming the games for readablility
Esports[Esports$Game == "Overwatch", c("Game")] <- "OW"
Esports[Esports$Game == "Counter-Strike: Global Offensive", c("Game")] <- "CSGO"
Esports[Esports$Game == "League of Legends", c("Game")] <- "LoL"
Esports[Esports$Game == "Heroes of the Storm", c("Game")] <- "HoTS" 
Esports[Esports$Game == "Hearthstone", c("Game")] <- "HS" 

Esports
```
```{r}
pieChartData <- data.frame(Genre = c("Battle Royale", "Collectible Card Game", "First-Person Shooter", "Multiplayer Online Battle Arena"),
                      TotalTournaments = c(sum(subset(Esports, Esports$Genre == "Battle Royale")$TotalTournaments), 
                                                  sum(subset(Esports, Esports$Genre == "Collectible Card Game")$TotalTournaments), 
                                                  sum(subset(Esports, Esports$Genre == "First-Person Shooter")$TotalTournaments),
                                                sum(subset(Esports, Esports$Genre == "Multiplayer Online Battle Arena")$TotalTournaments)),
                      total = c(sum(Esports$TotalTournaments))) %>%
                    mutate(labels = round((TotalTournaments/total) * 100, 1))

pieChartData

```


```{r}
#Calculating the total number of tournaments by game
totalTournOW <- sum(subset(Esports, Esports$Game == "OW")$TotalTournaments)
totalTournDota2 <- sum(subset(Esports, Esports$Game == "Dota 2")$TotalTournaments)
totalTournFN <- sum(subset(Esports, Esports$Game == "Fortnite")$TotalTournaments)
totalTournLoL <- sum(subset(Esports, Esports$Game == "LoL")$TotalTournaments)
totalTournCSGO <- sum(subset(Esports, Esports$Game == "CSGO")$TotalTournaments)
totalTournHoTS <- sum(subset(Esports, Esports$Game == "HoTS")$TotalTournaments)
totalTournPUBG <- sum(subset(Esports, Esports$Game == "PUBG")$TotalTournaments)
totalTournHS <- sum(subset(Esports, Esports$Game == "HS")$TotalTournaments)

# Calculating the total amount of prize miney won by game
totalPrizeOW <- sum(subset(Esports, Esports$Game == "OW")$TotalUSDPrize)
totalPrizeDota2 <- sum(subset(Esports, Esports$Game == "Dota 2")$TotalUSDPrize)
totalPrizeFN <- sum(subset(Esports, Esports$Game == "Fortnite")$TotalUSDPrize)
totalPrizeLoL <- sum(subset(Esports, Esports$Game == "LoL")$TotalUSDPrize)
totalPrizeCSGO <- sum(subset(Esports, Esports$Game == "CSGO")$TotalUSDPrize)
totalPrizeHoTS <- sum(subset(Esports, Esports$Game == "HoTS")$TotalUSDPrize)
totalPrizePUBG <- sum(subset(Esports, Esports$Game == "PUBG")$TotalUSDPrize)
totalPrizeHS <- sum(subset(Esports, Esports$Game == "HS")$TotalUSDPrize)

```


```{r}
#Setting up the new Dataframe that tells us the Total Prizes won and total tournaments by game
newData <- data.frame(Game = c("OW", "Dota 2", "Fortnite", "LoL", "CSGO", "HoTS", "PUBG", "HS"),
                      TotalTournamentsPerGame = c(totalTournOW, totalTournDota2, totalTournFN, totalTournLoL,
                                                  totalTournCSGO, totalTournHoTS, totalTournPUBG, totalTournHS), 
                      TotalPrizePerGame = c(totalPrizeOW, totalPrizeDota2, totalPrizeFN, totalPrizeLoL,
                                            totalPrizeCSGO, totalPrizeHoTS, totalPrizePUBG, totalPrizeHS))

newData
```


## Bar chart 
We want to see the 
```{r}
ggplot(data = Esports, mapping = aes(x = Game, y = TotalUSDPrize/100,  fill = Genre)) + 
  geom_col() +
  labs(title = "Total Prize Money Won by Game" ,
       subtitle = "Source: eSports Earnings Money earned by Players & Teams from eSports Tournaments" ,
       y = "Total Prize Money" ,
       x = "Game")
```


### Pie Chart of the Number of Tournaments per Game Genre 
```{r}
pie <- ggplot(data = pieChartData, mapping = aes(x= "", y = TotalTournaments, fill=Genre)) +
        geom_bar(width = 1, stat = "identity") +
        coord_polar("y", start = 0) +
            labs(title = "Number of Tournaments per Game Genre " ,
                  subtitle = "Source: eSports Earnings Money earned by Players & Teams from eSports Tournaments",
                  y = "Number of Tournaments",
                 caption = "*Blue = 40.8%     *Purple = 42.8%")
pie
```


```{r}
# Only grabbing teams that play multiple esports games
teamProgression <- filter(Esports, TeamName %in% c("Team Liquid", "Cloud9", "MVP", "Fnatic", 
                                                   "compLexity Gaming"))
teamProgression
```



### line plot of the number of the total earnings vs number of tournaments
```{r}
ggplot(data = teamProgression , aes(x = TotalTournaments , y = TotalUSDPrize/100)) +
        geom_line(aes(color = TeamName)) +
        geom_point(aes(alpha = Game), size = 1)  +
        labs(title = "Number of Tournaments vs Total Prize Money Won" ,
             subtitle = "Source: Kaggle",
             caption = "*Only teams that played multiple eSports were used in this analysis" ,
             x = "Total Number of Tournaments",
             y = "Total Prize Money Won" )

```




### scatterplot of the amount of money based on the release year of each game

```{r}
ggplot(data = newData, mapping = aes(x = TotalTournamentsPerGame, y = TotalPrizePerGame/100)) +
        geom_point(aes(color = Game)) +
        labs(title = "Total Amount of Tournaments vs. Total Prize Money Won" ,
             subtitle = "Source: Kaggle",
             y = "Total Prize Money Won",
             x = "Total Amount of Tournaments")
```


### Boxplot

```{r}
ggplot(data = teamProgression, mapping = aes(y = TotalTournaments, x = TeamName)) +
        geom_boxplot(aes(color = TeamName), show.legend = FALSE) +
        labs(title = "Total eSports Tournaments Played by Team",
             subtitle = "Source: Kaggle",
             x = "Team",
             y = "Number of Tournaments")
```


## Histogram
```{r}
ggplot(data = Esports, mapping = aes(x = TotalTournaments, fill = Genre)) +
        geom_histogram(binwidth = 5, color = "black") +
        geom_vline(aes(xintercept = mean(TotalTournaments)), color = "blue", linetype = "dashed") +
  labs(title = "Number of Tournaments each Team Competed In",
       subtitle = "Source: Kaggle",
       x = "Number Competitions Attended")
        
```


## Violin plot

```{r}
ggplot(data = teamProgression, mapping = aes(y = TotalTournaments, x = Genre)) +
        geom_violin(aes(fill = Genre), show.legend = FALSE) +
        stat_summary(fun.y = mean, geom = "point", size = 2, color = "brown", shape = 3) +
        labs(title = "Tournament Consistency by Genre",
             subtitle = "Source: Kaggle",
             x = "Genre",
             y = "Total Tournaments")
```


